### 2017-11-15 submission/manuscript.Rmd
add R package references

***Statistical Analysis:***
All statistical analysis after sequence processing utilized the R software package (v`r paste(version$major, ".", version$minor, sep = "")`). For the $\alpha$-diversity analysis, values were power transformed using the rcompanion (v`r paste(packageVersion("rcompanion")[1])`) package and then Z-score normalized using the car (v`r paste(packageVersion("car")[1])`) package. Testing for $\alpha$-diversity differences utilized linear mixed-effect models created using the lme4 (v`r paste(packageVersion("lme4"))[1]`) package to correct for study and variable region effects in feces and study, variable region, and individual effects in tissue. Relative risk was analyzed using both the epiR (v`r paste(packageVersion("epiR"))[1]`) and metafor (v`r paste(packageVersion("metafor"))[1]`) packages by assessing how many with and without disease were above and below the overall median value within the specific study. Relative risk significance testing utilized the chi-squred test. $\beta$-diversity differences utilized a Bray-Curtis distance matrix and PERMANOVA executed with the vegan (v`r paste(packageVersion("vegan"))[1]`) package. Random Forest models were built using both the caret (v`r paste(packageVersion("caret"))[1]`) and randomForest (v`r paste(packageVersion("randomForest"))[1]`) packages. Differences between the obtained AUC versus a random model AUC was assessed using T-tests. Power analysis and estimations were made using the pwr (v`r paste(packageVersion("pwr"))[1]`) and statmod (v`r paste(packageVersion("statmod"))[1]`) packages. All figures were created using both ggplot2 (v`r paste(packageVersion("ggplot2"))[1]`) and gridExtra (v`r paste(packageVersion("gridExtra"))[1]`) packages.

>>>>

***Statistical Analysis:***
All statistical analysis after sequence processing utilized the R (v`r paste(version$major, ".", version$minor, sep = "")`) software package [@r_citation_2017]. For the $\alpha$-diversity analysis, values were power transformed using the rcompanion (v`r paste(packageVersion("rcompanion")[1])`) package [@rcompanion_citation_2017] and then Z-score normalized using the car (v`r paste(packageVersion("car")[1])`) package [@car_citation_2011]. Testing for $\alpha$-diversity differences utilized linear mixed-effect models created using the lme4 (v`r paste(packageVersion("lme4"))[1]`) package [@lme4_citation_2015] to correct for study and variable region effects in feces and study, variable region, and individual effects in tissue. Relative risk was analyzed using both the epiR (v`r paste(packageVersion("epiR"))[1]`) and metafor (v`r paste(packageVersion("metafor"))[1]`) packages [@epir_citation_2017; @metafor_citation_2010] by assessing how many with and without disease were above and below the overall median value within the specific study. Relative risk significance testing utilized the chi-squred test. $\beta$-diversity differences utilized a Bray-Curtis distance matrix and PERMANOVA executed with the vegan (v`r paste(packageVersion("vegan"))[1]`) package [@vegan_citation_2017]. Random Forest models were built using both the caret (v`r paste(packageVersion("caret"))[1]`) and randomForest (v`r paste(packageVersion("randomForest"))[1]`) packages [@caret_citation_2017; @randomforest_citation_2002]. Differences between the obtained AUC versus a random model AUC was assessed using T-tests. Power analysis and estimations were made using the pwr (v`r paste(packageVersion("pwr"))[1]`) and statmod (v`r paste(packageVersion("statmod"))[1]`) packages [@pwr_citation_2017; @statmod_citation_2016]. All figures were created using both ggplot2 (v`r paste(packageVersion("ggplot2"))[1]`) and gridExtra (v`r paste(packageVersion("gridExtra"))[1]`) packages [@ggplot2_citation_2009; @gridextra_citation_2017].

### 2017-11-15 submission/manuscript.tex
add R package references

\textbf{\emph{Statistical Analysis:}} All statistical analysis after
sequence processing utilized the R software package (v3.4.2). For the
\(\alpha\)-diversity analysis, values were power transformed using the
rcompanion (v1.10.1) package and then Z-score normalized using the car
(v2.1.5) package. Testing for \(\alpha\)-diversity differences utilized
linear mixed-effect models created using the lme4 (v1.1.14) package to
correct for study and variable region effects in feces and study,
variable region, and individual effects in tissue. Relative risk was
analyzed using both the epiR (v0.9.87) and metafor (v2.0.0) packages by
assessing how many with and without disease were above and below the
overall median value within the specific study. Relative risk
significance testing utilized the chi-squred test. \(\beta\)-diversity
differences utilized a Bray-Curtis distance matrix and PERMANOVA
executed with the vegan (v2.4.4) package. Random Forest models were
built using both the caret (v6.0.77) and randomForest (v4.6.12)
packages. Differences between the obtained AUC versus a random model AUC
was assessed using T-tests. Power analysis and estimations were made
using the pwr (v1.2.1) and statmod (v1.4.30) packages. All figures were
created using both ggplot2 (v2.2.1) and gridExtra (v2.3) packages.

@@

>>>>

\textbf{\emph{Statistical Analysis:}} All statistical analysis after
sequence processing utilized the R (v3.4.2) software package {[}33{]}.
For the \(\alpha\)-diversity analysis, values were power transformed
using the rcompanion (v1.10.1) package {[}34{]} and then Z-score
normalized using the car (v2.1.5) package {[}35{]}. Testing for
\(\alpha\)-diversity differences utilized linear mixed-effect models
created using the lme4 (v1.1.14) package {[}36{]} to correct for study
and variable region effects in feces and study, variable region, and
individual effects in tissue. Relative risk was analyzed using both the
epiR (v0.9.87) and metafor (v2.0.0) packages {[}37,38{]} by assessing
how many with and without disease were above and below the overall
median value within the specific study. Relative risk significance
testing utilized the chi-squred test. \(\beta\)-diversity differences
utilized a Bray-Curtis distance matrix and PERMANOVA executed with the
vegan (v2.4.4) package {[}39{]}. Random Forest models were built using
both the caret (v6.0.77) and randomForest (v4.6.12) packages
{[}40,41{]}. Differences between the obtained AUC versus a random model
AUC was assessed using T-tests. Power analysis and estimations were made
using the pwr (v1.2.1) and statmod (v1.4.30) packages {[}42,43{]}. All
figures were created using both ggplot2 (v2.2.1) and gridExtra (v2.3)
packages {[}44,45{]}.

@@

\hypertarget{ref-r_citation_2017}{}
33. R Core Team. R: A language and environment for statistical computing
{[}Internet{]}. Vienna, Austria: R Foundation for Statistical Computing;
2017. Available from: \url{https://www.R-project.org/}

\hypertarget{ref-rcompanion_citation_2017}{}
34. Mangiafico S. Rcompanion: Functions to support extension education
program evaluation {[}Internet{]}. 2017. Available from:
\url{https://CRAN.R-project.org/package=rcompanion}

\hypertarget{ref-car_citation_2011}{}
35. Fox J, Weisberg S. An R companion to applied regression
{[}Internet{]}. Second. Thousand Oaks CA: Sage; 2011. Available from:
\url{http://socserv.socsci.mcmaster.ca/jfox/Books/Companion}

\hypertarget{ref-lme4_citation_2015}{}
36. Bates D, Mächler M, Bolker B, Walker S. Fitting linear mixed-effects
models using lme4. Journal of Statistical Software. 2015;67:1--48.

\hypertarget{ref-epir_citation_2017}{}
37. Telmo Nunes MS with contributions from, Heuer C, Marshall J, Sanchez
J, Thornton R, Reiczigel J, et al. EpiR: Tools for the analysis of
epidemiological data {[}Internet{]}. 2017. Available from:
\url{https://CRAN.R-project.org/package=epiR}

\hypertarget{ref-metafor_citation_2010}{}
38. Viechtbauer W. Conducting meta-analyses in R with the metafor
package. Journal of Statistical Software {[}Internet{]}. 2010;36:1--48.
Available from: \url{http://www.jstatsoft.org/v36/i03/}

\hypertarget{ref-vegan_citation_2017}{}
39. Oksanen J, Blanchet FG, Friendly M, Kindt R, Legendre P, McGlinn D,
et al. Vegan: Community ecology package {[}Internet{]}. 2017. Available
from: \url{https://CRAN.R-project.org/package=vegan}

\hypertarget{ref-caret_citation_2017}{}
40. Jed Wing MKC from, Weston S, Williams A, Keefer C, Engelhardt A,
Cooper T, et al. Caret: Classification and regression training
{[}Internet{]}. 2017. Available from:
\url{https://CRAN.R-project.org/package=caret}

\hypertarget{ref-randomforest_citation_2002}{}
41. Liaw A, Wiener M. Classification and regression by randomForest. R
News {[}Internet{]}. 2002;2:18--22. Available from:
\url{http://CRAN.R-project.org/doc/Rnews/}

\hypertarget{ref-pwr_citation_2017}{}
42. Champely S. Pwr: Basic functions for power analysis {[}Internet{]}.
2017. Available from: \url{https://CRAN.R-project.org/package=pwr}

\hypertarget{ref-statmod_citation_2016}{}
43. Giner G, Smyth GK. Statmod: Probability calculations for the inverse
gaussian distribution. R Journal. 2016;8:339--51.

\hypertarget{ref-ggplot2_citation_2009}{}
44. Wickham H. Ggplot2: Elegant graphics for data analysis
{[}Internet{]}. Springer-Verlag New York; 2009. Available from:
\url{http://ggplot2.org}

\hypertarget{ref-gridextra_citation_2017}{}
45. Auguie B. GridExtra: Miscellaneous functions for ``grid'' graphics
{[}Internet{]}. 2017. Available from:
\url{https://CRAN.R-project.org/package=gridExtra}
